---
title: "Assignment1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Parliment Data Set
```{r}
parliment <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/2 Data Visualization/parliament.csv")
parliment
```

```{r}
library(dplyr)
library(ggplot2)
```

# - For top ten parties compute the following metrics for the year 2009
```{r}
prty <- parliment %>% filter(YEAR==2009,Position==1) %>% group_by(PARTY) %>% summarize(com=n()) %>% arrange(desc(com)) %>% head(10) 
prty

prty1 = prty$PARTY
prty1

topprty <- parliment %>% filter(PARTY %in% prty1)
topprty
```

```{r Total number of contestants}
cont <- topprty %>% filter(PARTY==prty1, YEAR==2009) %>% group_by(PARTY) %>% summarize(con=n())
cont
```

```{r  - Total of number of winning seats}
winn <- topprty %>% filter(YEAR==2009,Position==1) %>% group_by(PARTY) %>% summarize(win=n())
winn
```

```{r - Avg. %of votes}

per_vot <- topprty %>% filter(YEAR==2009) %>% group_by(PARTY) %>% summarize(VOTES=sum(VOTES)) %>% mutate(per=VOTES/sum(VOTES)*100)
per_vot

```

- Identify top ten candidates with highest %margin of votes for the year 2009
- Identify year wise percentage of male and female candidates?


### ODI Batting
- Create a new column by binning the Runs column using the following ranges and plot the frequency count of ranges
  - 0-25, 26-50, 51-75, 76-100, 100+
- Consider the top ten players by total runs and compute and visualize the number of centuries across years (use facet_grid or facet_wrap)

### Tweets (#narendramodi)

### Tweets(#flipkart)

```{r}
nowins <- parliment %>% group_by(YEAR,PARTY) %>% filter(Position==1,PARTY %in% prty1) %>% summarize(noofwins= n())
nowins
```

```{r}
ggplot(nowins,aes(x=PARTY,y=noofwins)) + geom_bar(stat = 'identity') + facet_wrap(~YEAR)
```



```{r}
ggplot(nowins,aes(x=YEAR,y=noofwins)) + geom_bar(stat = 'identity') + facet_wrap(~PARTY)
```

```{r}
nowins$YEAR = as.factor(nowins$YEAR)
ggplot(nowins,aes(x=YEAR,y=PARTY, fill= -noofwins)) + geom_tile()
```

#top no of candidates wins
```{r top can}
can_win <- parliment %>% group_by(NAME,YEAR) %>% filter(Position==1) %>% summarize(nofwins = n()) %>% arrange(desc(nofwins)) %>% head(10)
can_win
```
```{r}
ggplot(can_win,aes(y=YEAR,x=NAME,fill=-nofwins)) + geom_tile()
```

```{r}
top_candidate <- parliment %>% filter(Position==1) %>% group_by(NAME) %>% summarise(winsss = sum(Position)) %>% arrange(-winsss) %>% head(10)
top_candidate
```

```{r}
tp_cndt <- parliment %>% filter( NAME %in% top_candidate$NAME,Position==1) %>% group_by(YEAR,NAME) %>% summarize(wins = n())
tp_cndt
```

```{r}
tp_cndt$YEAR = as.factor(tp_cndt$YEAR)
ggplot(tp_cndt,aes(x=YEAR,y=NAME,fill=-wins)) + geom_tile()
```




