---
title: "Application using Shiny"
runtime: shiny
output: 
 flexdashboard::flex_dashboard:
   orientation: rows
   vertical_layout: scroll
   theme: cerulean #theme
---

```{r}
#theme http://rmarkdown.rstudio.com/flexdashboard/using.html#appearance
library(flexdashboard)
library(dplyr)
library(ggplot2)
```

Sidebar {.sidebar}
==============================

```{r}
fileInput(inputId = "meta_data",label = "Please Upload a csv File")
uiOutput("dropdown_columns") #Used to display UIdropdown all columns after uploading
#uiOutput("dropdown_numcolumns") #Used to display UIdropdown all columns after uploading
#uiOutput("dropdown_catgcolumns") #Used to display UIdropdown all columns after uploading
```

EDA
==================================
Row
----------------------------------

```{r}
### Upload file path details shown can upload only lessthan 5MB file
#renderTable({input$meta_data})
```

### Uploaded Data details
```{r}
tableOutput("data_preview")
```

Row
----------------------------------

### Number of rows
```{r}
textOutput("nrows")
```

### Number of columns
```{r}
textOutput("ncols")
```

Row
----------------------------------

### Column Names
```{r}
tableOutput("colnames")
```

### Numeric Columns
```{r}
tableOutput("numericcolumns")
```

### Categorical Columns
```{r}
tableOutput("catogoricalcolumns")
```

```{r}
observe({
 if(is.null(input$meta_data))                #checking the path is null or havin path
return(NULL)
 data=read.csv(input$meta_data$datapath)     #Retriving/reading data from path datapath
 output$data_preview=renderTable(head(data)) #Storing render data to data_preview
 output$nrows=renderText(nrow(data))         #Number rows count
 output$ncols=renderText(ncol(data))         #Number columns count
 output$colnames=renderTable(names(data))    #Columns Names
 nums <- sapply(data, is.numeric)            #Identifying Numeric and catagorical columns
 numerics<-names(data)[nums]
 output$numericcolumns=renderTable(names(data)[nums])       #retriving only Numeric columns