---
title: "Excercise-1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
parliment <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/2 Data Visualization/parliament.csv")
parliment 
```

```{r}
library(dplyr)
library(ggplot2)
```

# - For top ten parties compute the following metrics for the year 2009
```{r}
prty <- parliment %>% filter(YEAR==2009,Position==1) %>% group_by(PARTY) %>% summarize(com=n()) %>% arrange(desc(com)) %>% head(10) 
prty

prty1 = prty$PARTY
prty1

topprty <- parliment %>% filter(PARTY %in% prty1)
topprty
```

```{r Total number of contestants}
cont <- topprty %>% filter(PARTY==prty1, YEAR==2009) %>% group_by(PARTY) %>% summarize(con=n())
cont
```

```{r  - Total of number of winning seats}
winn <- topprty %>% filter(YEAR==2009,Position==1) %>% group_by(PARTY) %>% summarize(win=n())
winn
```

```{r - Avg. %of votes}

per_vot <- topprty %>% filter(YEAR==2009) %>% group_by(PARTY) %>% summarize(VOTES=sum(VOTES)) %>% mutate(per=VOTES/sum(VOTES)*100)
per_vot

```

- Identify top ten candidates with highest %margin of votes for the year 2009
- Identify year wise percentage of male and female candidates?

ODI Batting
```{r}
cricket <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/2 Data Visualization/updated_odi_batting.csv")
cricket 
```

Create a new column by binning the Runs column using the following ranges and plot the frequency count of ranges
0-25, 26-50, 51-75, 76-100, 100+
```{r}
cricket <- cricket %>% mutate(binning=if_else(Runs>=0 &))
```

Consider the top ten players by total runs and compute and visualize the number of centuries across years (use facet_grid or facet_wrap)
Compute total number of breaks taken by each player and identify top five players. (Note: A break is considered, if a player has not played any match in a year)
For top ten players (based on total runs) compute the following metrics
Total runs
Total centuries
Total Fifties
Total Ducks
Total experience in terms of number of years they have played
Tweets (#narendramodi)

Monthwise total number of tweets in a bar chart
Create a new column for quarter and compute quarter wise total number of tweets from each quarter
Create a new column to identify the number of hashtags and compute device-wise average number of retweets
Create a stacked bar chart to visualize month-wise total number of tweets from each device
Create a scatter plot with the following details
X axis contains number of retweets
Y axis contains number of likes
Color represents device from which it was tweeted
Create a heat map or tile plot to visualize number of tweets by day of month and month of the year
