---
title: "od"
author: "Theja"
date: "30 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggmap)
library(gganimate)
library(dplyr)
library(devtools)
library(animation)
library(gapminder)
library(ggplot2)
```

```{r}
odi <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/2 Data Visualization/odi.csv")
odi$Country <- as.character(odi$Country)
country <- unique(odi$Country)
country_code <- geocode(country)

geocode_state <- cbind(country,country_code)
head(geocode_state, n=50)
```

```{r}
```{r geting map }
parliament$STATE=as.character(parliament$STATE)
state=unique(parliament$STATE)
state_code=geocode(state)

geocode_state=cbind(state,state_code)
head(geocode_state)
#write.csv(geocode_state,"geocode_state.csv",row.names = FALSE) 
# In csv file concatenate lat and long by (=concatenate(c2,",",b2)) then copy the whole column and paste in the plotmap points field in darrinward.com/lat-long, and get the map
```



